\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-26 OaklandSubmission/ld.tex
fig 8
circuit compilation

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{mult}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \bval \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Is environ misplaced? Can we merge base value and circuit gate?}}
\label{fig:circuits}
\end{figure}

@@

\divya{Start here....}
\noindent\textbf{Evaluation to Circuit.} \figureref{eval-inter-circ} shows the judgments for the evaluation of the intermediate language to a circuit. We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow
\val$. 
%
Rules ({\sc{S-PAdd}}) and ({\sc{S-SAdd}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PAdd}}) evaluates a public addition $\widetilde{e_{1}}
+_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} + n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SAdd}}) evaluates a secret addition $\widetilde{e_{1}}
+_{\mathcal{A}} \widetilde{e_{2}}$ to an arithmetic add
gate $\kw{add}\:\kappa_{1}\:\kappa_{2}$. Foreshadowing on the
compilation rules to be presented later, the target
expressions from our compiler never have $\widetilde{e_{1}}
+_{\mathcal{B}} \widetilde{e_{2}}$, as our compiler is aware that $+$
is more performant using arithmetic circuit, rather than a boolean
one. Rules ({\sc{S-PCond}}) and ({\sc{S-SCond}})
are along the similar lines. Rule ({\sc{S-PCond}}) evaluates a public
conditional to the value from one of the branches, while the rule
({\sc{S-SCond}}) evaluates to a \kw{mux} gate that takes input
circuits from the conditional ($\kappa_{1}$) and both the branches
($\kappa_{2}$ and $\kappa_{3}$). Once again for performance reasons,
the target expressions from our compiler do not have
$\lcond{\mathcal{A}}{e_{1}}{e_{2}}{e_{3}}$. Rules
({\sc{S-Coerce}}) and ({\sc{S-Inp}}) evaluate to the coerce and input
gates respectively.

Statement evaluation $\widetilde{\rho} \vdash \widetilde{s} \Downarrow
\widetilde{\rho}_{1}; \chi$ evaluates a target statement to produce a new
environment $\widetilde{\rho}_{1}$, and a circuit $\chi$. $\chi$ (shown
in Figure~\ref{fig:tgtlang}) is either empty, \kw{bind}-ing of a
circuit gate $\kappa$ to range $r$, \kw{out} gate, or a sequence of
circuits. Rules ({\sc{S-DeclC}}), ({\sc{S-DeclCkt}}), and
({\sc{S-DeclCktA}}) show the variable declaration cases. Rule
({\sc{S-DeclC}}) shows the case when $\widetilde{e}$ evaluates to
$\widetilde{v}$, where $\widetilde{v}$ is either a constant or an
array of constants. In this case, the mapping $x \mapsto
\widetilde{v}$ is added to the environment, and the resulting circuit
is empty. When 
$\widetilde{e}$ evaluates to a circuit $\kappa$, rule
({\sc{S-DeclCkt}}) picks a fresh $r$, adds the mapping $x \mapsto r$
to the environment, and outputs the circuit
$\kw{bind}\:\kappa\:r$. Rule ({\sc{S-DeclCktA}}) is analogous for
$\widetilde{e}$ evaluating to an array of circuits. The variable
assignment rules (not shown in the figure) are similar. Rule
({\sc{S-WriteCkt}}) shows the case for writing to an array, where the
array contents are secret. Finally, rule ({\sc{S-Out}}) compiles to an
\kw{out} circuit.

\begin{figure}
  \small
  \fbox{$\widetilde{\rho} \vdash \widetilde{e} \Downarrow \widetilde{v}$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{S-Var}}]
               {
               }
               {
                 \widetilde{\rho} \vdash x \Downarrow \widetilde{\rho}(x)
               }

    \inferrule*[lab={\footnotesize{S-PAdd}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow n_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} +_{\mathcal{P}} \widetilde{e_{2}} \Downarrow n_{1} + n_{2}
               }

    \inferrule*[lab={\footnotesize{S-Read}}]
               {
                 \widetilde{\rho} \vdash x \Downarrow [\overline{\bval_i}]_{n_{1}} \\\\
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow n \quad n < n_{1}
               }
               {
                 \widetilde{\rho} \vdash x[\widetilde{e}] \Downarrow \bval_n
               }\\\\
    \inferrule*[lab={\footnotesize{S-SAdd}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \kappa_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} +_{\mathcal{A}} \widetilde{e_{2}} \Downarrow \kw{add}\:\kappa_{1}\:\kappa_{2}
               }

@@

    \inferrule*[lab={\footnotesize{S-SGt}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \kappa_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} >_{\mathcal{B}} \widetilde{e_{2}} \Downarrow \kw{gt}\:\kappa_{1}\:\kappa_{2}
               }\\\\
               \inferrule*[lab={\footnotesize{S-SCond}}]
               {
                 \forall i \in \{1, 2, 3\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \kappa_{i}
               }
               {
                 \widetilde{\rho} \vdash \lcond{\mathcal{B}}{\widetilde{e_{1}}}{\widetilde{e_{2}}}{\widetilde{e_{3}}} \Downarrow \kw{mux}\:\kappa_{1}\:\kappa_{2}\:\kappa_{3}
               }
               \hspace{0.2cm}
    \inferrule*[lab={\footnotesize{S-Coerce}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \widetilde{v}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e} \rhd m \Downarrow \widetilde{v} \rhd m
               }
               \\\\
               %% \inferrule*[lab={\footnotesize{S-Arr}}]
               %% {
               %%   \forall i \in \{0 \dots n - 1\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \widetilde{w_{i}}
               %% }
               %% {
               %%   \widetilde{\rho} \vdash [\overline{\widetilde{e_{i}}}]_{n} \Downarrow [\overline{\widetilde{w_{i}}}]_{n}
               %% }

               \inferrule*[lab={\footnotesize{S-PCond}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow c\\\\
                 c = \top \Rightarrow \widetilde{e'} = \widetilde{e_{1}}\\
                 c = \bot \Rightarrow \widetilde{e'} = \widetilde{e_{2}}\\\\
                 \widetilde{\rho} \vdash \widetilde{e'} \Downarrow \widetilde{v}
               }
               {
                 \widetilde{\rho} \vdash \lcond{\mathcal{P}}{\widetilde{e}}{\widetilde{e_{1}}}{\widetilde{e_{2}}} \Downarrow \widetilde{v}
               }
               %\hspace{0.5cm}

    \inferrule*[lab={\footnotesize{S-Inp}}]
               {
               }
               {
                 \widetilde{\rho} \vdash \kw{in}^{m}_{j} \Downarrow \kw{in}^{m}_{j}
               }
  \end{array}
  \]
  \\\\
    \fbox{$\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho'}; \chi$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{S-DeclC}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \widetilde{v}\\\\
                 \widetilde{v} = c \vee \widetilde{v} = [\overline{c_{i}}]_{n}\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}, x \mapsto \widetilde{v}
               }
               {
                 \widetilde{\rho} \vdash \tau\:x = \widetilde{e} \Downarrow \widetilde{\rho}_{1}; \cdot
               }

@@

    \inferrule*[lab={\footnotesize{S-DeclCkt}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \kappa\quad
                 \mathsf{fresh}\:r\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}, x \mapsto r\quad
                 \chi = \kw{bind}\:\kappa\:r
               }
               {
                 \widetilde{\rho} \vdash \tau\:x = \widetilde{e} \Downarrow \widetilde{\rho}_{1}; \chi
               }

\\\\
    \inferrule*[lab={\footnotesize{S-DeclCktA}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow [\overline{\kappa_{i}}]_{n}\\\\
                 \forall i \in \{0 \dots n - 1\}.\:\mathsf{fresh}\:r_{i}\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}, x \mapsto [r_{i}]_{n}\quad
                 \chi = \overline{\kw{bind}\:\kappa_{i}\:r_{i}}
               }
               {
                 \widetilde{\rho} \vdash \tau\:x = \widetilde{e} \Downarrow \widetilde{\rho}_{1}; \chi
               }

@@

    \inferrule*[lab={\footnotesize{S-Out}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \kappa
               }
               {
                 \widetilde{\rho} \vdash \kw{out}\:\widetilde{e} \Downarrow \widetilde{\rho}; \kw{out}\:\kappa
               }

               \\\\
    \inferrule*[lab={\footnotesize{S-If}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow c\\\\
                 c = \top \Rightarrow \widetilde{s} = \widetilde{s_{1}}\\\\
                 c = \bot \Rightarrow \widetilde{s} = \widetilde{s_{2}}\\\\
                 \widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi
               }
               {
                 \widetilde{\rho} \vdash \ite{\widetilde{e}}{\widetilde{s_{1}}}{\widetilde{s_{2}}} \Downarrow \widetilde{\rho}_{1}; \chi
               }

@@

    \inferrule*[lab={\footnotesize{S-WriteCkt}}]
               {
                 \widetilde{\rho} \vdash x \Downarrow [\overline{r_{i}}]_{n}\quad
                 \widetilde{\rho} \vdash \widetilde{e_{1}} \Downarrow n_{1}\\\\
                 n_{1} < n\quad
                 \mathsf{fresh}\:r\quad
                 \widetilde{\rho} \vdash \widetilde{e_{2}} \Downarrow \kappa\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}[x \mapsto [\overline{r_{i}}]_{n}[n_{1} \mapsto r]]
               }
               {
                 \widetilde{\rho} \vdash x[\widetilde{e_{1}}] := \widetilde{e_{2}} \Downarrow \widetilde{\rho}_{1}; \kw{bind}\:\kappa\:r
               }

@@

@@

\subsubsection*{Circuit semantics} The target semantics produces a
circuit to compute over the secret data using an MPC protocol. \nc{We use 2PC and MPC interchangeably. I guess its fine?}With
our circuit semantics, we model the \emph{functional} aspect of the
protocol, parametrized by the sharing functions.

>>>>

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{mult}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \bval \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    %\ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Can we merge base value and circuit gate?}}
\label{fig:circuits}
\end{figure}

@@

\begin{figure}[t]
  \small
  \fbox{$\widetilde{\rho} \vdash \widetilde{e} \Downarrow \val$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{S-Var}}]
               {
               }
               {
                 \widetilde{\rho} \vdash x \Downarrow \widetilde{\rho}(x)
               }

    \inferrule*[lab={\footnotesize{S-PMult}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow n_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} \mulop_{\mathcal{P}} \widetilde{e_{2}} \Downarrow n_{1} \mulop n_{2}
               }

    \inferrule*[lab={\footnotesize{S-Read}}]
               {
                 \widetilde{\rho} \vdash x \Downarrow [\overline{\wire_i}]_{n_{1}} \\\\
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow n \quad n < n_{1}
               }
               {
                 \widetilde{\rho} \vdash x[\widetilde{e}] \Downarrow \bval_n
               }\\\\
    \inferrule*[lab={\footnotesize{S-SMult}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \gate_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} \mulop_{\mathcal{A}} \widetilde{e_{2}} \Downarrow \kw{mult}\:\gate_{1}\:\gate_{2}
               }

@@

    \inferrule*[lab={\footnotesize{S-SGt}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \gate_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} >_{\mathcal{B}} \widetilde{e_{2}} \Downarrow \kw{gt}\:\gate_{1}\:\gate_{2}
               }\\\\
               \inferrule*[lab={\footnotesize{S-SCond}}]
               {
                 \forall i \in \{1, 2, 3\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \gate_{i}
               }
               {
                 \widetilde{\rho} \vdash \lcond{\mathcal{B}}{\widetilde{e_{1}}}{\widetilde{e_{2}}}{\widetilde{e_{3}}} \Downarrow \kw{mux}\:\gate_{1}\:\gate_{2}\:\gate_{3}
               }
               \hspace{0.2cm}
    \inferrule*[lab={\footnotesize{S-Coerce}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \val
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e} \rhd m \Downarrow \val \rhd m
               }
               \\\\
               %% \inferrule*[lab={\footnotesize{S-Arr}}]
               %% {
               %%   \forall i \in \{0 \dots n - 1\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \widetilde{w_{i}}
               %% }
               %% {
               %%   \widetilde{\rho} \vdash [\overline{\widetilde{e_{i}}}]_{n} \Downarrow [\overline{\widetilde{w_{i}}}]_{n}
               %% }

               \inferrule*[lab={\footnotesize{S-PCond}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow c\\\\
                 c = \top \Rightarrow \widetilde{e'} = \widetilde{e_{1}}\\
                 c = \bot \Rightarrow \widetilde{e'} = \widetilde{e_{2}}\\\\
                 \widetilde{\rho} \vdash \widetilde{e'} \Downarrow \val
               }
               {
                 \widetilde{\rho} \vdash \lcond{\mathcal{P}}{\widetilde{e}}{\widetilde{e_{1}}}{\widetilde{e_{2}}} \Downarrow \val
               }
               %\hspace{0.5cm}

    \inferrule*[lab={\footnotesize{S-Inp}}]
               {
               }
               {
                 \widetilde{\rho} \vdash \kw{in}^{m}_{j} \Downarrow \kw{in}^{m}_{j}
               }
  \end{array}
  \]
  \\\\
    \fbox{$\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho_1}; \crct$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{S-DeclC}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \val\\\\
                 \left(\val = c\right) \vee \left(\val = [\overline{c_{i}}]_{n}\right)\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}, x \mapsto \val
               }
               {
                 \widetilde{\rho} \vdash \tau\:x = \widetilde{e} \Downarrow \widetilde{\rho}_{1}; \cdot
               }

@@

    \inferrule*[lab={\footnotesize{S-DeclCkt}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \gate\quad
                 \mathsf{fresh}\:\wire\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}, x \mapsto \wire\quad
                 \crct = \kw{bind}\:\gate\:\wire
               }
               {
                 \widetilde{\rho} \vdash \tau\:x = \widetilde{e} \Downarrow \widetilde{\rho}_{1}; \crct
               }

\\\\
    \inferrule*[lab={\footnotesize{S-DeclCktA}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow [\overline{\gate_{i}}]_{n}\\\\
                 \forall i \in [n].\:\mathsf{fresh}\:\wire_{i}\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}, x \mapsto [\overline{\wire_{i}}]_{n}\quad
                 \crct = \overline{\kw{bind}\:\gate_{i}\:\wire_{i}}
               }
               {
                 \widetilde{\rho} \vdash \tau\:x = \widetilde{e} \Downarrow \widetilde{\rho}_{1}; \chi
               }

@@

    \inferrule*[lab={\footnotesize{S-Out}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \gate
               }
               {
                 \widetilde{\rho} \vdash \kw{out}\:\widetilde{e} \Downarrow \widetilde{\rho}; \kw{out}\:\gate
               }

               \\\\
    \inferrule*[lab={\footnotesize{S-If}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow c\\\\
                 c = \top \Rightarrow \widetilde{s} = \widetilde{s_{1}}\\\\
                 c = \bot \Rightarrow \widetilde{s} = \widetilde{s_{2}}\\\\
                 \widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \crct
               }
               {
                 \widetilde{\rho} \vdash \ite{\widetilde{e}}{\widetilde{s_{1}}}{\widetilde{s_{2}}} \Downarrow \widetilde{\rho}_{1}; \crct
               }

@@

    \inferrule*[lab={\footnotesize{S-WriteCkt}}]
               {
                 \widetilde{\rho} \vdash x \Downarrow [\overline{\wire_{i}}]_{n}\quad
                 \widetilde{\rho} \vdash \widetilde{e_{1}} \Downarrow n_{1}\\\\
                 n_{1} < n\quad
                 \mathsf{fresh}\:\wire\quad
                 \widetilde{\rho} \vdash \widetilde{e_{2}} \Downarrow \gate\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}[x \mapsto ([\overline{\wire_{i}}]_{n}[n_{1} \mapsto \wire])]
               }
               {
                 \widetilde{\rho} \vdash x[\widetilde{e_{1}}] := \widetilde{e_{2}} \Downarrow \widetilde{\rho}_{1}; \kw{bind}\:\gate\:\wire
               }

@@

\subsubsection*{Evaluation to Circuit} \figureref{eval-inter-circ} shows the judgments for the evaluation of the intermediate language to a circuit. 
The runtime environment is defined as follows:

\vspace{0.2cm}
$
\small
\begin{array}{rrcl}
    \ftext{Runtime environment} & \widetilde\rho &::=& \cdot \mid \rho,x \mapsto \val\\
\end{array}
$
\vspace{0.2cm}

We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow\val$. 
%
Rules ({\sc{S-PMult}}) and ({\sc{S-SMult}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PMult}}) evaluates a public multiplication $\widetilde{e_{1}}
\mulop_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} \mulop n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SMult}}) evaluates a secret multiplication $\widetilde{e_{1}}
\mulop_{\mathcal{A}} \widetilde{e_{2}}$ to an arithmetic multiplication
gate $\kw{mult}\:\gate_{1}\:\gate_{2}$. As mentioned above, the intermediate language
expressions generated by our compiler never have $\widetilde{e_{1}}
\mulop_{\mathcal{B}} \widetilde{e_{2}}$, as our compiler is aware that $\mulop$
is more performant using an arithmetic circuit compared to a boolean
one. Rules ({\sc{S-PCond}}) and ({\sc{S-SCond}})
are along the similar lines. Rule ({\sc{S-PCond}}) evaluates a public
conditional to the value from one of the branches, while the rule
({\sc{S-SCond}}) evaluates to a \kw{mux} gate that takes input
circuits from the guard ($\gate_{1}$) and both the branches
($\gate_{2}$ and $\gate_{3}$). Once again for performance reasons,
the target expressions from our compiler do not have
$\lcond{\mathcal{A}}{e_{1}}{e_{2}}{e_{3}}$. Rules
({\sc{S-Coerce}}) and ({\sc{S-Inp}}) evaluate to the coerce and input
gates respectively.

Statement evaluation $\widetilde{\rho} \vdash \widetilde{s} \Downarrow
\widetilde{\rho}_{1}; \chi$ evaluates statements $\widetilde{s}$ to produce a new
environment $\widetilde{\rho}_{1}$, and a circuit $\crct$. A circuit $\crct$ (shown
in \figureref{circuits}) is either empty, \kw{bind}-ing of a
circuit gate $\gate$ to wire $\wire$, \kw{out} gate, or a sequence of
circuits. Rules ({\sc{S-DeclC}}), ({\sc{S-DeclCkt}}), and
({\sc{S-DeclCktA}}) show the variable declaration cases. Rule
({\sc{S-DeclC}}) shows the case when $\widetilde{e}$ evaluates to
$\val$, where $\val$ is either a constant or an
array of constants. In this case, the mapping $x \mapsto
\val$ is added to the environment, and the resulting circuit
is empty. When 
$\widetilde{e}$ evaluates to a circuit $\gate$, rule
({\sc{S-DeclCkt}}) picks a fresh wire $\wire$, adds the mapping $x \mapsto \wire$
to the environment $\widetilde{\rho}$, and outputs the circuit
$\kw{bind}\:\gate\:\wire$. Rule ({\sc{S-DeclCktA}}) is analogous for
$\widetilde{e}$ evaluating to an array of circuits. The variable
assignment rules (not shown in the figure) are similar. Rule
({\sc{S-WriteCkt}}) shows the case for writing to an array, where the
array contents are secret. Finally, rule ({\sc{S-Out}}) compiles to an
\kw{out} circuit.

\divya{Start here...}
\subsubsection*{Circuit semantics} The target semantics produces a
circuit to compute over the secret data using an MPC protocol. \nc{We use 2PC and MPC interchangeably. I guess its fine?}With
our circuit semantics, we model the \emph{functional} aspect of the
protocol, parametrized by the sharing functions.

@@
